%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------
\pdfinfoomitdate=1
\pdfsuppressptexinfo=1
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Matthew Champagne} \\ \vspace{3pt}
    \small
    \faAt \hspace{.5pt} \href{mailto:champagne7103@gmail.com}{champagne7103@gmail.com}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/Allotec}{GitHub}
    $|$
    \faMapMarker \hspace{.5pt} \href{https://goo.gl/maps/89WDCuaor1qhY7JVA}{New York}
\end{center}



%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Stony Brook University}{Stony Brook, NY}
      {B.E Computer Engineering;   }{Aug 2019 \textbf{--} May 2023}
    \resumeSubheading
      {Stony Brook University}{Stony Brook, NY}
      {M.S Computer Engineering;   }{Aug 2023 \textbf{--} May 2025}
    
  \resumeSubHeadingListEnd

%----------- WORK EXPERIENCE -----------

\section{Work Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Orbit International Corporation}{Hauppauge, NY, USA}
      {Junior Embedded Systems Design Engineer}{May 2023 \textbf{--} Current}
        \resumeItemListStart
            \resumeItem{Lead the software development effort for multiple projects including new and legacy products.}
            \resumeItem{Setup, documented, and maintained a self-hosted GitLab server for Orbit Instrument's Engineering department.}
            \resumeItem{Helped migrate our sister company from SVN to Gitlab. }
        \resumeItemListEnd
    
    \resumeSubheading
      {Orbit International Corporation}{Hauppauge, NY, USA}
      {Embedded Systems Design Engineer Intern}{Jan 2023 \textbf{--} May 2023}
        \resumeItemListStart
            \resumeItem{Constructed a trackball demo unit to test the feasibility of using an optical sensor for our trackball products. }
            \resumeItem{Learned how to use Orbit's product lifecycle software, schematic software, and product release process. }
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd

%----------- PROJECTS -----------
\section{Work Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
        {\textbf{Rockwell Collins Simulated Control Display Unit (SCDU) and Supporting Software (C++ and Rust)} }{}
          \resumeItemListStart
            \resumeItem{The SCDU is a smart display capable of displaying graphics, text, and reporting back user input using a custom protocol over UDP. }
            \resumeItem{To make the SCDU, drivers were written to control backlighting, scan for key presses, and perform end-user firmware upgrades via the serial port using Ymodem. }
            \resumeItem{To support the customer and production, a cross platform desktop application was written to light balance the keypad, perform firmware upgrades, and sanitize the unit over USB.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{BAE Systems Upgraded Radio Control Unit (uRCU) Software Upgrade (C On AVR)} }{}
          \resumeItemListStart
            \resumeItem{The uRCU is a smart display unit that is responsible for communicating with BAE's transponder and providing feedback to the helicopter pilot. }
            \resumeItem{This program was under DO-178C rules therefore I was given requirements that I had to implement, test, trace, and document. }
            \resumeItem{The existing codebase lacked source control, so I wrote a Python script to gather all old versions and import them into a Git repository. }
          \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{BAE Systems Slim Data Entry Device (DED) (Rust on STM32)} }{}
          \resumeItemListStart
            \resumeItem{The Slim DED is a VT100 terminal emulator that recieves characters / ANSI escape codes over the serial port and renders the data onto the grid. }
            \resumeItem{Additionally, the unit had to support end-user firmware upgrades, touch screen input, and contrast adjustment. }
            \resumeItem{Wrote the main application, bootloader, and cross platform desktop testing application. }
          \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{OIL \href{https://govtribe.com/file/government-file/fy22c5isrcmoss-victory-spec-doc-v1-9-dist-a-a787-dot-pdf}{VICTORY Bus} Prototype (C++ on Linux)} }{}
          \resumeItemListStart
            \resumeItem{The OIL Prototype unit was a touch screen device that used GPS data from the 
              \href{https://govtribe.com/file/government-file/fy22c5isrcmoss-victory-spec-doc-v1-9-dist-a-a787-dot-pdf}{VICTORY Bus} 
              to determine the current location on an open source mapping application. }
            \resumeItem{Wrote a reusable and modular 
              \href{https://govtribe.com/file/government-file/fy22c5isrcmoss-victory-spec-doc-v1-9-dist-a-a787-dot-pdf}{VICTORY Bus} 
              Library. }
            \resumeItem{Wrote a Systemd service that monitored the network for 
              \href{https://govtribe.com/file/government-file/fy22c5isrcmoss-victory-spec-doc-v1-9-dist-a-a787-dot-pdf}{VICTORY Bus} 
              packets to send them over to the open source map application. }
          \resumeItemListEnd
      
    \resumeSubHeadingListEnd

%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Programming:}{ C, C++, Java, Python, Verilog, SystemVerilog, VHDL, SystemC, Rust, Latex} \\ \vspace{3pt}
        
        \textbf{Technologies:}{ Linux, GitLab, STM32, CMake, AVR, GCC, Networking} \\ \vspace{3pt}
    }}
  \resumeSubHeadingListEnd

\end{document}
